---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r pkg-knitr-opts, include=FALSE}
hrbrpkghelpr::global_opts()
```

```{r badges, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::stinking_badges()
```

```{r description, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::yank_title_and_description()
```

## What's Inside The Tin

The following functions are implemented:

```{r ingredients, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::describe_ingredients()
```

## TODO

Support the offline [bloom filter searches](https://circl.lu/services/hashlookup/#querying-hashlookup-without-online-queries).

## Installation

```{r install-ex, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::install_block()
```

## Usage

```{r lib-ex}
library(hashlookup)
library(gt)

# current version
packageVersion("hashlookup")

```

### Hash lookup API info

```{r info}
hl_info()
```

### Individual lookups

```{r individual-01}
hl_query("8ED4B4ED952526D89899E723F3488DE4", "md5") %>% gt::gt()
```

```{r individual-02}
hl_query("FFFFFDAC1B1B4C513896C805C2C698D9688BE69F", "sha1") %>% gt::gt()
```

```{r individual-03}
hl_query("301c9ec7a9aadee4d745e8fd4fa659dafbbcc6b75b9ff491d14cbbdd840814e9", "sha256") %>% str()
```

### Bulk lookups

```{r bulk-01}
hl_query(
  hash = c(
    "6E2F8616A01725DCB37BED0A2495AEB2",
    "8ED4B4ED952526D89899E723F3488DE4",
    "344428FA4BA313712E4CA9B16D089AC4"
  ),
  type = "md5"
) %>% 
  gt::gt()
```

```{r bulk-02}
hl_query(
  hash = c(
    "FFFFFDAC1B1B4C513896C805C2C698D9688BE69F",
    "FFFFFF4DB8282D002893A9BAF00E9E9D4BA45E65",
    "FFFFFE4C92E3F7282C7502F1734B243FA52326FB"
  ),
  type = "sha1"
) %>% 
  gt::gt()
```

## hashlookup Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a Contributor Code of Conduct. 
By participating in this project you agree to abide by its terms.
